Analysing the Performance of Shallow-Water Models with the Roofline Model

### 2017-09-06 docs/papers/roofline_habakkuk/habakkuk.tex
habakkuk-paper: add skeleton to conclusions, toc

@@

Shallow implementation of Sadourny~\cite{sadourny75}.
NEMOLite2D.

@@

@@

>>>>

\tableofcontents

@@

\begin{itemize}
\item Shallow implementation of Sadourny~\cite{sadourny75}.
\item NEMOLite2D.
\item NEMO
\end{itemize}

@@

\section{Building a Model of a CPU Core}

We require various parameters that characterise the performance of a
CPU core, the value of these are micro-architecture dependent.

\begin{itemize}
\item Vector width
\item Size of a cache line
\item Support for FMA
\item Support for out-of-order execution
\item Available Instruction-Level Parallelism
\item Cost of arithmetic operations
\end{itemize}

\subsection{Micro-Benchmarks}

\begin{itemize}
\item Fortran for high-level, intrinsic ops (e.g. SIN())
\item Likwid for low-level, individual arithmetic ops (e.g. floating-point division)
\item Results from Agner Fog
\end{itemize}

@@

\begin{itemize}

\item Constructing a traditional roofline model is not that straightforward.

\item We have demonstrated that the upper bounds in such a model can be
  unrealistically high and therefore not that useful in determining
  the performance-limiting aspects of a kernel.

\item We have developed a tool, Habakkuk, which parses Fortran source
  code and generates various performance estimates using a simple
  model of the microarchitecture of the target CPU.

\item Using the resulting performance estimates as the ceilings in the
  roofline model results in more accurate bounds and provides more
  information to a developer seeking to optimise their source code.

\end{itemize}
